Model LF

### 2022-09-20 Estimation.Rmd
commit

plot(komp_r_obs)
```

@@

# Txt. for model

## model

S_model.txt="MODEL

COMMENT> Pricing Nexus

COMMENT> 
IDENTITY> pg
EQ> LOG(pg) = 0.840852289293*LOG(pc) - 0.0401650251402 +
pg_adj

COMMENT> 
IDENTITY> p_bd
EQ> LOG(p_bd) = 0.988897636487*LOG(pc) + 0.0286611434831 +
p_bd_adj

COMMENT> 
IDENTITY> p_equip
EQ> LOG(p_equip) = 0.304376220161*LOG(pc) + 0.0160136953595
+ p_equip_adj

COMMENT> 
IDENTITY> px
EQ> LOG(px) = 0.638216896739*LOG(pc) - 0.012650117362 +
px_adj

COMMENT> Households

COMMENT> 
IDENTITY> int_r_h
EQ> int_r_h = TSLAG(idep,1)*TSLAG(iba_h,1)  + TSLAG(ibd,1)*TSLAG(sec_h,1)  + int_r_h_adj

COMMENT> 
IDENTITY> int_p_h
EQ> int_p_h =  - TSLAG(iloan,1)*TSLAG(l_h,1)  + int_p_h_adj

COMMENT> 
IDENTITY> div_h
EQ> div_h = d_20124*((TSLAG(eq_h_nf,1) + TSLAG(eq_h_f,1))*TSLAG(divd,1) + TSLAG(eq_h_row,1)*TSLAG(diva,1)) + (1-d_20124)*(TSLAG(eq_h,1)*TSLAG(divd,1)) +  div_h_adj

COMMENT> 
IDENTITY> aa_check
EQ> aa_check = TSLAG(eq_h_f,1)*TSLAG(divd,1)

COMMENT> 
IDENTITY> insu_h
EQ> insu_h = TSLAG(ins_h,1)*TSLAG(insu,1) + ins_h_adj

COMMENT>  property income H
IDENTITY> propinc_r_h
EQ> propinc_r_h = int_r_h + div_h + insu_h + res_r_h

COMMENT> ' property expenditure H
IDENTITY> propinc_p_h
EQ> propinc_p_h = int_p_h + res_p_h

COMMENT> 
IDENTITY> npropinc_h
EQ> npropinc_h = propinc_r_h - propinc_p_h

COMMENT> Gross income H
IDENTITY> yh_h
EQ> yh_h = w_h_r + b2_h_r + (npropinc_h )

COMMENT> 
IDENTITY> yh2a
EQ> yh2a = propinc_r_h + b2_h_r

COMMENT> 
IDENTITY> yh2b
EQ> yh2b = - propinc_p_h

COMMENT> 
IDENTITY> yh1
EQ> yh1 = w_h_r +  nsben_h + oth_h

COMMENT> 
IDENTITY> w_h_r
EQ> w_h_r = wage * emp

COMMENT> ' property income part of the disposable income (capitalists)
IDENTITY> yd2a_h
EQ> yd2a_h =(1 - tax_rate2)*(yh2a)

COMMENT> 
IDENTITY> yd2b_h
EQ> yd2b_h = (1 - tax_rate2)*(yh2b)

COMMENT> age and benefits part of the disposable income (workers) / tax_h_adj is added here because of the relative size versus yh2
IDENTITY> yd1_h
EQ> yd1_h =(1 - tax_rate1)*(yh1) - tax_h_adj

COMMENT> 
IDENTITY> tax_h
EQ> tax_h = -(tax_rate2*(yh2a+yh2b) +  tax_rate1*yh1 +  tax_h_adj)

COMMENT> 
IDENTITY> yd1_hk
EQ> yd1_hk = yd1_h/pc

COMMENT> 
IDENTITY> yd2a_hk
EQ> yd2a_hk = yd2a_h/pc

COMMENT> 
IDENTITY> yd2b_hk
EQ> yd2b_hk = yd2b_h/pc

COMMENT> Disposable income
IDENTITY> yd_h
EQ> yd_h = yd1_h + yd2a_h + yd2b_h

COMMENT> 
IDENTITY> nsben_h
EQ> nsben_h = nben_h - d8_h

COMMENT> Disposable income (redundant for now)
IDENTITY> yd_h1
EQ> yd_h1 = yh_h + tax_h + nben_h

COMMENT> 
IDENTITY> yd_hk
EQ> yd_hk = yd1_hk + yd2a_hk + yd2b_hk

COMMENT> 
IDENTITY> yd_hk_ds
EQ> yd_hk_ds = yd1_hk_ds + yd2a_hk_ds + yd2b_hk

COMMENT> 
IDENTITY> yd1_hk_ds
EQ> yd1_hk_ds = yd1_hk - (alpha_100 + alpha_101*SD1 + alpha_102*SD2 + alpha_103*SD3) + mean_yd1_hk

COMMENT> 
IDENTITY> yd2a_hk_ds
EQ> yd2a_hk_ds  = yd2a_hk  - (alpha_110 + alpha_111*SD1 + alpha_112*SD2 + alpha_113*SD3) + mean_yd2a_hk

COMMENT> Savings H
IDENTITY> s_h
EQ> s_h = yd_h - pcon + d8_h

COMMENT> Sectoral balance
IDENTITY> nl_h
EQ> nl_h = s_h - i_h - np_h + ctr_h

COMMENT> 
BEHAVIORAL> pconk_ds
TSRANGE 2006 2 2020 1
EQ> TSDELTALOG(pconk_ds) = C_1 + C_2*TSLAG(LOG(pconk_ds),1) + C_3*TSLAG(LOG(yd1_hk_ds),1) + C_4*LOG(TSLAG(yd2a_hk_ds,1) + TSLAG(yd2b_hk,1)) + C_5*TSLAG(LOG(fnw_hk),2) + C_6*TSDELTALOG(TSLAG(pconk_ds,2)) + C_7*TSDELTALOG(TSLAG(pconk_ds,3)) + C_8*TSDELTALOG(yd1_hk_ds)  + C_9*TSDELTALOG(yd2a_hk_ds + yd2b_hk) + C_10*d_2008q4 + C_11*d_2018q2 + C_12*d_2020q1 + C_13* time
COEFF> C_1 C_2 C_3 C_4 C_5 C_6 C_7 C_8 C_9 C_10 C_11 C_12 C_13
STORE> coe(1)

COMMENT> 
IDENTITY> pconk
EQ> pconk = pconk_ds + alpha_00 + alpha_01*SD1 + alpha_02*SD2 + alpha_03*SD3 - mean_pconk

COMMENT> nominal private consumption
IDENTITY> pcon
EQ> pcon = pconk*pc

COMMENT>  
BEHAVIORAL> i_bd_h_k_ds
TSRANGE 2006 3 2020 1
EQ> LOG(i_bd_h_k_ds) = P_620 + 
P_621*TSDELTALOG(TSLAG(i_bd_h_k_ds,1)/TSLAG(bd_h_k,2))+ 
P_622*TSDELTALOG(TSLAG(i_bd_h_k_ds,3)/TSLAG(bd_h_k,4))+ 
P_623*TSDELTALOG(TSLAG(p_bd,1)/TSLAG(pi_1,1)) + 
P_624*TSDELTALOG(TSLAG(p_bd,2)/TSLAG(pi_1,2)) + 
P_625*TSDELTALOG(TSLAG(yd_hk_ds,2)/TSLAG(bd_h_k,3))+ 
P_626*TSDELTALOG(TSLAG(-l_h,1)/TSLAG(bd_h,2)) + 
P_627*LOG(TSLAG(i_bd_h_k_ds,1)/TSLAG(bd_h_k,2)) + 
P_628*LOG(TSLAG(yd_hk_ds,1)/TSLAG(bd_h_k,2)) + 
P_629*LOG(TSLAG(p_bd,1)/TSLAG(pi_1,1)) +
P_630*LOG(TSLAG(-l_h,1)/TSLAG(bd_h,2)) + 
P_631*d_2006q4 + 
P_632*d_2014q4 + 
alpha_1*LOG(TSLAG(bd_h_k,1)) + 
alpha_2* TSLAG(LOG(i_bd_h_k_ds),1) + 
alpha_3* TSLAG(-LOG(bd_h_k),2)
COEFF> P_620 P_621 P_622 P_623 P_624 P_625 P_626 P_627 P_628 P_629 P_630 P_631 P_632 alpha_1 alpha_2 alpha_3
RESTRICT> alpha_1 = 1
alpha_2 = 1
alpha_3 = 1
STORE> coe(2)

COMMENT> 
IDENTITY> i_bd_h_k
EQ> i_bd_h_k = i_bd_h_k_ds + (alpha_10 + alpha_11*SD1 + alpha_12*SD2 + alpha_13*SD3) - mean_i_bd_h_k

COMMENT> 
BEHAVIORAL> i_equip_h_k_ds
TSRANGE 2006 2 2020 1
EQ> LOG(i_equip_h_k_ds) = p_636 + p_637 * TSDELTALOG(TSLAG(i_equip_h_k_ds,1)/TSLAG(equip_h_k,2)) + p_638 * TSDELTALOG(TSLAG(i_equip_h_k_ds,2)/TSLAG(equip_h_k,3)) + p_639*TSDELTALOG(yd_hk_ds/TSLAG(equip_h_k,1)) + p_640*dummy_4 + alpha_1* TSLAG(LOG(i_equip_h_k_ds),1) + alpha_2* TSLAG(LOG(equip_h_k),1) + alpha_3* TSLAG(-LOG(equip_h_k),2)
COEFF> p_636 p_637 p_638 p_639 p_640 alpha_1 alpha_2 alpha_3
RESTRICT> alpha_1 = 1
alpha_2 = 1
alpha_3 = 1 
STORE> coe(3)

COMMENT> 
IDENTITY> i_equip_h_k
EQ>  i_equip_h_k = i_equip_h_k_ds + alpha_20 + alpha_21*SD1 + alpha_22*SD2 + alpha_23*SD3 - mean_i_equip_h_k

COMMENT> tilføjet
IDENTITY> nben_h
EQ>  nben_h = nben_h_rest + nben_h_un

COMMENT> tilføjet
IDENTITY> komp_r
EQ>  komp_r = (dp_person/wage_trim)

COMMENT> tilføjet
IDENTITY> nben_h_un
EQ>  nben_h_un = dp_person*unemp*kuld

COMMENT> tilføjet
IDENTITY> dp_person
EQ>  dp_person = 0.9507*max_dp

COMMENT> tilføjet
IDENTITY> wage_trim
EQ>  wage_trim = w_h_r_trim/emp

COMMENT> tilføjet
IDENTITY> w_h_r_trim
EQ>  w_h_r_trim = w_h_r

COMMENT> tilføjet
BEHAVIORAL> nben_h_rest
TSRANGE 2005 4 2020 1
EQ> TSDELTALOG(nben_h_rest) = P_671 + P_672*TSDELTALOG(zaland_jesper) + P_673*TSDELTA(unemp) + P_674*TSDELTA(TSLAG(unemp,1)) +   P_675*LOG(TSLAG(nben_h_rest,1)) + P_676*TSLAG(unemp,1) + P_677*LOG(TSLAG(zaland_jesper,1)) 
COEFF> P_671 P_672 P_673 P_674 P_675 P_676 P_677 
STORE> coe(4)

COMMENT> Financial side

COMMENT> 
IDENTITY> l_h_tr
EQ> l_h_tr= l_h_tr_ratio * (-yd_hk_ds*pc)

COMMENT> Mangler stadig at få tilpasset til ik diff
BEHAVIORAL> l_h_tr_ratio
TSRANGE 2006 2 2020 1
EQ> TSDELTA(l_h_tr_ratio) = p_646 
+ p_641*TSDELTA(TSLAG(l_h_tr_ratio,2))
+ p_642*TSDELTA(iloan) 
+ p_643*TSDELTALOG(TSLAG(i_bd_h_k_ds,3)/TSLAG(yd_hk_ds,3)) 
+ p_644* TSLAG(l_h_tr_ratio,1) 
+ p_645*LOG(TSLAG(-l_h,2)/TSLAG(yd_hk_ds,2)*TSLAG(pc,2)) 
+ p_647*d_2007q34 
+ p_648*time
COEFF> p_646 p_641 p_642 p_643 p_644 p_645 p_647 p_648
STORE>  coe(5)

COMMENT> 
IDENTITY> iba_h
EQ> iba_h= TSLAG(iba_h,1) + iba_h_tr + iba_h_rvx

COMMENT> For the time being we take sec_h_tr as exogenous. It is assumed that households' holdings of securities are entirely issued by the government.
IDENTITY> sec_h
EQ> sec_h= TSLAG(sec_h,1) + sec_h_tr + sec_h_rvx

COMMENT> 
IDENTITY> sec_h_tr_g
EQ> sec_h_tr_g=sec_h_tr

COMMENT> 
IDENTITY> l_h
EQ> l_h= TSLAG(l_h,1) + l_h_tr + l_h_rvx

COMMENT> 
IDENTITY> eq_h
EQ> eq_h= eq_h_ratio*(TSLAG(eq_h,1) +TSLAG(sec_h,1)+  TSLAG(iba_h,1)) + eq_h_rvx

COMMENT> 
BEHAVIORAL> eq_h_ratio
TSRANGE 2006 1 2020 1
EQ> TSDELTA(eq_h_ratio) =  p_770  
+ p_771* TSDELTA(TSLAG(ibd,1))
+ p_772* TSDELTA(TSLAG(ratio_in_eq_h,1))
+ p_773* TSLAG(eq_h_ratio,1)
+ p_774* TSLAG(ibd,1) 
+ p_775* TSLAG(ratio_in_eq_h,2)
COEFF> p_770 p_771 p_772 p_773 p_774 p_775
STORE> coe(6)

COMMENT> 
IDENTITY> eq_h_tr
EQ> eq_h_tr = TSDELTA(eq_h) - eq_h_rvx

COMMENT> 
IDENTITY> iba_h_tr
EQ> iba_h_tr = nl_h - l_h_tr - eq_h_tr  - sec_h_tr - ins_h_tr + nl_h_adj

COMMENT> 
IDENTITY> eq_h_nf
EQ> eq_h_nf = d_20124*alpha_nf *eq_h

COMMENT> 
IDENTITY> eq_h_f
EQ> eq_h_f = d_20124*alpha_f *eq_h

COMMENT> 
IDENTITY> eq_h_row
EQ> eq_h_row = d_20124*alpha_row*eq_h

COMMENT> 
IDENTITY> eq_h_nf_tr
EQ> eq_h_nf_tr = TSDELTA(eq_h_nf) - eq_h_nf_rvx

COMMENT> 
IDENTITY> eq_h_f_tr
EQ> eq_h_f_tr = TSDELTA(eq_h_f) - eq_h_f_rvx

COMMENT> 
IDENTITY> eq_h_row_tr
EQ> eq_h_row_tr = TSDELTA(eq_h_row) - eq_h_row_rvx

COMMENT> 
IDENTITY> eq_h_test
EQ> eq_h_test = eq_h - (eq_h_nf + eq_h_f + eq_h_row)

COMMENT> 
IDENTITY> ins_h
EQ> ins_h= TSLAG(ins_h,1) + ins_h_tr + ins_h_rvx

COMMENT> 
IDENTITY> ins_h_tr
EQ> ins_h_tr = d8_h + ins_h_tr_excl_d8

COMMENT> 
BEHAVIORAL> d8_h
TSRANGE 2005 4 2020 1
EQ> TSDELTALOG(d8_h) = p_701*TSDELTALOG(TSLAG(d8_h,1)) + p_702*TSDELTALOG(w_h_r) + p_703*TSDELTALOG(TSLAG(old_age_ratio,1)) + p_704*LOG(TSLAG(d8_h,1)) + p_705*LOG(TSLAG(w_h_r,1)) + p_706*LOG(TSLAG(old_age_ratio,1)) + p_707*d_2014q3
COEFF> p_701 p_702 p_703 p_704 p_705 p_706 p_707
STORE> coe(7)

COMMENT> 
IDENTITY> lev_h
EQ> lev_h = l_h/yd_h

COMMENT> NET WEALTH AND FINANCIAL NET WEALTH

COMMENT> 
IDENTITY> fa_h
EQ> fa_h = iba_h + sec_h + eq_h + ins_h

COMMENT> 
IDENTITY> fnw_h
EQ> fnw_h = fa_h  + l_h

COMMENT> 
IDENTITY> fnw_hk
EQ> fnw_hk = fnw_h/pc

COMMENT> Capital Account

COMMENT>gross fixed capital formation (buildings and dwellings)
IDENTITY> i_bd_h
EQ> i_bd_h = i_bd_h_k * p_bd

COMMENT> gross fixed capital formation (equipment)
IDENTITY> i_equip_h
EQ> i_equip_h = i_equip_h_k * p_equip

COMMENT> Real net stock of buildings and dwellings
IDENTITY> bd_h_k
EQ> TSDELTA(bd_h_k) = i_bd_h_k - TSLAG(bd_h_k,1) * delta_bd_h

COMMENT>  Real net stock of equipment
IDENTITY> equip_h_k
EQ> TSDELTA(equip_h_k) = i_equip_h_k - TSLAG(equip_h_k,1) * delta_equip_h

COMMENT> Nominal net stock of buildings and dwellings
IDENTITY> bd_h
EQ> TSDELTA(bd_h) = i_bd_h + TSLAG(bd_h_k,1) * (1-delta_bd_h)*TSDELTA(p_bd) - TSLAG(bd_h_k,1) * delta_bd_h * p_bd

COMMENT> Nominal net stock of equipment
IDENTITY> equip_h
EQ> TSDELTA(equip_h) = i_equip_h + TSLAG(equip_h_k,1) * (1-delta_equip_h)*TSDELTA(p_equip) - TSLAG(equip_h_k,1) * delta_equip_h * p_equip

COMMENT> NON-FINANCIAL SECTOR

COMMENT> Real side

COMMENT> 
IDENTITY> y
EQ> y = pcon + g + i + x - m

COMMENT> real sales
IDENTITY> yk
EQ> yk = pconk + ik + gk + xk - mk

COMMENT> real sales
IDENTITY> yk_ds
EQ> yk_ds = yk - (alpha_90 + alpha_91*SD1 + alpha_92* SD2 + alpha_93*SD3)+ mean_yk

COMMENT> 
IDENTITY> sk
EQ> sk= pconk + ik + gk + xk

COMMENT> real government consumption
IDENTITY> gk
EQ> gk = g/pg

COMMENT> nominal export
IDENTITY> x
EQ> x = xk*px

COMMENT> 
IDENTITY> rer
EQ> rer = pc*xr/pf

COMMENT> 
BEHAVIORAL> xk_ds
TSRANGE 2006 3 2020 1
EQ> TSDELTALOG(xk_ds) =  p_652*TSDELTALOG(TSLAG(gdp_tp,4)) + p_653*TSDELTALOG(rer) + p_654*LOG(TSLAG(xk_ds,1)) + p_655*LOG(TSLAG(gdp_tp,1)) + p_656*LOG(TSLAG(rer,2)) + p_657*d_2008q2 + p_658*d_2018q1 + p_659*d_2019q3 + p_660* time
COEFF>  p_652 p_653 p_654 p_655 p_656 p_657 p_658 p_659 p_660
STORE> coe(8)

COMMENT> 
IDENTITY> xk
EQ> xk = xk_ds + alpha_80 + alpha_81*SD1 + alpha_82*SD2 + alpha_83*SD3 - mean_xk

COMMENT> nominal import
IDENTITY> m
EQ> m = mk*pm

COMMENT> 
BEHAVIORAL> mk_ds
TSRANGE 2006 2 2020 1
EQ> TSDELTALOG(mk_ds) = p_661 + p_662*TSDELTALOG(TSLAG(mk_ds,2)) + p_663*TSDELTALOG(TSLAG(rer,1)) + p_664*TSDELTALOG(TSLAG(rer,3)) + p_665*TSDELTALOG(yk_ds) + p_666*LOG(TSLAG(mk_ds,1)) + p_667*LOG(TSLAG(yk_ds,1)) + p_668*d_2009q1 + p_669*d_2009q4
COEFF> p_661 p_662 p_663 p_664 p_665 p_666 p_667 p_668 p_669
STORE> coe(9)

COMMENT> 
IDENTITY> mk
EQ> mk = mk_ds + alpha_70 + alpha_71*SD1 + alpha_72*SD2 + alpha_73*SD3 - mean_mk

COMMENT> GDP deflator
IDENTITY> py
EQ> py = y/yk

COMMENT> nominal sales
IDENTITY> s
EQ> s = pcon + g + i + x

COMMENT> wage bill paid by NFC
IDENTITY> w_nf
EQ> w_nf = w_h_r +  (w_row_r - w_row_p)

COMMENT> Gross operating surplus received by the NFC
IDENTITY> b2_nf_r
EQ> b2_nf_r = b2 - (b2_h_r + b2_f_r + b2_g_r)

COMMENT> 
IDENTITY> yf
EQ> yf = y-((p_tax+p_tax_row)-(p_sub+p_sub_row))

COMMENT> 
IDENTITY> b2
EQ> b2 = yf - w_nf

COMMENT> wage share
IDENTITY> ws
EQ> ws = w_nf/yf  * zz

COMMENT> profit share
IDENTITY> ps
EQ> ps = 1 - ws

COMMENT> Rate of capacity utilization
IDENTITY> u
EQ> u=yk/(bd_nfc_k+equip_nfc_k)

COMMENT> Profit rate
IDENTITY> prate
EQ> prate=s_nf/(TSLAG(bd_nfc,1)+TSLAG(equip_nfc,1))

COMMENT> Profit rate
IDENTITY> prate_ds
EQ> prate_ds = prate - (alpha_120 + alpha_121*SD1 + alpha_122*SD2 + alpha_123*SD3) + mean_prate

COMMENT> Profit rate
IDENTITY> ps_ds 
EQ> ps_ds  = ps - (alpha_130 + alpha_131*SD1 + alpha_132*SD2 + alpha_133*SD3) + mean_ps

COMMENT> 
IDENTITY> tobinq
EQ> tobinq = (eq_nf_l) / (equip_nfc + bd_nfc)

COMMENT> Er fixet
BEHAVIORAL> i_bd_nfc_k_ds
TSRANGE 2006 1 2020 1
EQ> LOG(i_bd_nfc_k_ds) = p_800 + 
p_801*TSDELTALOG(TSLAG(i_bd_nfc_k_ds,1)/TSLAG(bd_nfc_k,2)) + 
p_802*TSDELTALOG(ps_ds) + 
p_803*TSDELTALOG(u_ds) + 
p_804* LOG(TSLAG(i_bd_nfc_k_ds,1)/TSLAG(bd_nfc_k,2)) + 
p_805 * LOG(TSLAG(ps_ds,1)) + 
p_806 * LOG(TSLAG(u_ds,1)) + 
p_807 * TSDELTALOG(tobinq) +
p_808 * LOG(TSLAG(tobinq,1)) +
alpha_1*TSLAG(LOG(i_bd_nfc_k_ds),1) + 
alpha_2*TSLAG(LOG(bd_nfc_k),1) + 
alpha_3*TSLAG(-LOG(bd_nfc_k),2)
COEFF> p_800 p_801 p_802 p_803 p_804 p_805 p_806 p_807 p_808 alpha_1 alpha_2 alpha_3
RESTRICT> alpha_1 = 1
alpha_2 = 1
alpha_3 = 1
STORE> coe(10)

COMMENT> 
IDENTITY> i_bd_nfc_k
EQ> i_bd_nfc_k = i_bd_nfc_k_ds + (alpha_30 + alpha_31*SD1 + alpha_32*SD2 + alpha_33*SD3) - mean_i_bd_nfc_k

COMMENT> 
IDENTITY> i_equip_nfc_k
EQ> i_equip_nfc_k = i_equip_nfc_k_ds + (alpha_40 + alpha_41*SD1 + alpha_42*SD2 + alpha_43*SD3) - mean_i_equip_nfc_k

COMMENT> 
IDENTITY> ik
EQ> ik =  i_equip_h_k + i_equip_nfc_k  +  i_equip_g_k + i_equip_fc_k +  i_bd_h_k + i_bd_nfc_k  +  i_bd_g_k  + i_bd_fc_k + i_adj_h_k + i_adj_nfc_k + i_adj_fc_k + i_adj_g_k

COMMENT> 
IDENTITY> i_h
EQ> i_h = i_equip_h_k*p_equip +  i_bd_h_k*p_bd  + i_adj_h_k*p_equip

COMMENT> 
IDENTITY> i_nf
EQ> i_nf = i_equip_nfc_k*p_equip +  i_bd_nfc_k*p_bd  + i_adj_nfc_k*p_equip

COMMENT> 
IDENTITY> i_f
EQ> i_f = i_equip_fc_k*p_equip +  i_bd_fc_k*p_bd  + i_adj_fc_k*p_equip

COMMENT> 
IDENTITY> i_g
EQ> i_g = i_equip_g_k*p_equip +  i_bd_g_k*p_bd  + i_adj_g_k*p_equip

COMMENT> 
IDENTITY> i
EQ> i = i_nf + i_f + i_g + i_h

COMMENT> 
BEHAVIORAL> i_equip_nfc_k_ds
TSRANGE 2006 1 2020 1
EQ> LOG(i_equip_nfc_k_ds) = p_807 + p_808 * TSDELTALOG(TSLAG(i_equip_nfc_k_ds,1)/TSLAG(equip_nfc_k,2)) + p_809 * TSDELTALOG(ps_ds) + p_810 * TSDELTALOG(u_ds) + p_811 *  LOG(TSLAG(i_equip_nfc_k_ds,1)/TSLAG(equip_nfc_k,2)) + p_812 * LOG(TSLAG(ps_ds,1)) + p_813 * LOG(TSLAG(u_ds,1)) + p_814 * dummy_10 + p_815 * dummy_11 + p_890*TSDELTALOG(tobinq) + p_891*LOG(TSLAG(tobinq,1)) + alpha_1*TSLAG(LOG(i_equip_nfc_k_ds),1) + alpha_2*TSLAG(LOG(equip_nfc_k),1) + alpha_3*TSLAG(-LOG(equip_nfc_k),2)
COEFF> p_807 p_808 p_809 p_810 p_811 p_812 p_813 p_814 p_815 p_890 p_891 alpha_1 alpha_2 alpha_3
RESTRICT> alpha_1 = 1
alpha_2 = 1
alpha_3 = 1
STORE> coe(11)

COMMENT> 
IDENTITY> int_nf
EQ> int_nf = (TSLAG(idep,1)*TSLAG(iba_nf,1) + TSLAG(ibd,1)*TSLAG(sec_nf,1) + TSLAG(iloan,1)*TSLAG(l_nf,1))

COMMENT> 
IDENTITY> div_nf
EQ> div_nf =d_20124*(((TSLAG(eq_nf_a_nf,1) + TSLAG(eq_nf_a_f,1) - TSLAG(eq_nf_l_nf,1) + TSLAG(eq_h_nf,1)+ TSLAG(eq_row_a_nf,1) + TSLAG(eq_f_a_nf,1) + TSLAG(eq_g_nf,1)))* TSLAG(divd,1) + TSLAG(eq_nf_a_row,1)*TSLAG(diva,1)) + (1-d_20124)*(TSLAG(neq_nf,1)*TSLAG(divd,1)) + div_nf_adj

COMMENT> 
IDENTITY> insu_nf
EQ> insu_nf =  TSLAG(ins_nf,1)*TSLAG(insu,1)

COMMENT> 
IDENTITY> npropinc_nf
EQ> npropinc_nf = int_nf + int_nf_adj + div_nf + insu_nf + ins_nf_adj + (res_r_nf ) - (res_p_nf)

COMMENT> gross income NFC Ændret yil den anden i modellen 
IDENTITY> yh_nf
EQ> yh_nf = y + b2_nf_r - b2 - (p_tax + p_tax_row) + (p_sub+p_sub_row) - w_nf + (propinc_r_nf - propinc_p_nf)

COMMENT> savings NFC TAX_NF is negative
IDENTITY> s_nf
EQ> s_nf = yh_nf + tax_nf + oth_nf

COMMENT> 
IDENTITY> tax_nf
EQ> tax_nf = -tax_rate_nf*y

COMMENT> Sectoral balance NFC
IDENTITY> nl_nf
EQ> nl_nf = s_nf - i_nf - np_nf + ctr_nf

COMMENT> Financial side

COMMENT> Change in stocks

COMMENT> iba
IDENTITY> iba_nf
EQ> iba_nf = TSLAG(iba_nf,1) + iba_nf_tr + iba_nf_rvx

COMMENT> 
IDENTITY> iba_nf_tr
EQ> iba_nf_tr = nl_nf + nl_nf_adj - neq_nf_tr - l_nf_tr - sec_nf_tr - ins_nf_tr

COMMENT> SEC . For the time being, we take sec_nf_tr as exogenous.
IDENTITY> sec_nf
EQ> sec_nf = TSLAG(sec_nf,1) + sec_nf_tr + sec_nf_rvx

COMMENT>  Loans
IDENTITY> l_nf
EQ> l_nf = TSLAG(l_nf,1) + l_nf_tr + l_nf_rvx

COMMENT> CHANGE in STOCKS OF EQUITIES:

COMMENT> Equities held as assets by NFC
IDENTITY> eq_nf_a
EQ> eq_nf_a = (1-d_20124)*(TSLAG(eq_nf_a,1) + eq_nf_a_tr + eq_nf_a_rvx)  + d_20124*eq_nf_ax

COMMENT> 
IDENTITY> eq_nf_a_nf
EQ> eq_nf_a_nf = d_20124 * (TSLAG(eq_nf_a_nf,1) + eq_nf_a_nf_tr + eq_nf_a_nf_rv)

COMMENT> equiteies NFC-NFC asset is obviously equal to equities NFC-NFC liability
IDENTITY> eq_nf_l_nf
EQ> eq_nf_l_nf = eq_nf_a_nf

COMMENT> this is the data for quities as assets for NFC viz-a-viz counter parties, e.g., NFC purchase equities from NFC, FC, and RoW
IDENTITY> eq_nf_ax
EQ> eq_nf_ax =  eq_nf_a_nf + eq_nf_a_f + eq_nf_a_row

COMMENT> 
IDENTITY> eq_nf_a_f
EQ> eq_nf_a_f = d_20124 * (TSLAG(eq_nf_a_f,1) + eq_nf_a_f_tr + eq_nf_a_f_rv)

COMMENT> 
IDENTITY> eq_nf_a_row
EQ> eq_nf_a_row = d_20124 * (TSLAG(eq_nf_a_row,1) + eq_nf_a_row_tr + eq_nf_a_row_rv)

COMMENT> total gross liabilities of equities on firms balance sheet is defined as the sum of NFC-NFC asset + the sum of NFC equities held by other sectors
IDENTITY> eq_nf_l
EQ> eq_nf_l = (1- d_20124)*(TSLAG(eq_nf_l,1) + eq_nf_l_tr + eq_nf_l_rvx)   +  d_20124*eq_nf_lx

COMMENT> total gross liabilities of equities on firms balance sheet is defined as the sum of NFC-NFC asset + the sum of NFC equities held by other sectors
IDENTITY> eq_nf_lx
EQ> eq_nf_lx =   eq_nf_a_nf + eq_h_nf + eq_row_a_nf + eq_f_a_nf + eq_g_nf

COMMENT> 
IDENTITY> neq_nf
EQ> neq_nf =d_20123*(-alpha_neq_nf * i_nf) + d_20124*( (eq_nf_a_f+ eq_nf_a_row)-(eq_f_a_nf + eq_g_nf + eq_h_nf + eq_row_a_nf))

COMMENT> 
IDENTITY> neq_nf_tr
EQ> neq_nf_tr = TSDELTA(neq_nf)-(neq_nf_rvx)

COMMENT>Some consistency check eqs:

COMMENT> this variable should be zero after 2012 and onwards as it captures the difference between equities as assets for nfc (aggregate) data minus equities as assets for NFC held at difference sectors after 2012. In short, after 2012, we can identify the counter parties where NFC are holding stocks.
IDENTITY> eq_nf_a_test
EQ> eq_nf_a_test = eq_nf_a - eq_nf_ax

COMMENT> this variable should be zero after 2012 and onwards as it captures the difference between equities as liabilities for nfc (aggregate) data minus equities as liabilities for NFC held at difference sectors after 2012. 
IDENTITY> eq_nf_l_test
EQ> eq_nf_l_test = eq_nf_l - eq_nf_lx

COMMENT> insurance NFC
IDENTITY> ins_nf
EQ> ins_nf = TSLAG(ins_nf,1) + ins_nf_tr + ins_nf_rvx

COMMENT> FINANCIAL NET WEALTH

COMMENT> net financial wealth
IDENTITY> fnw_nf
EQ> fnw_nf = iba_nf + eq_nf_a - eq_nf_l + sec_nf +l_nf + ins_nf

COMMENT> 
IDENTITY> fnw_nfk
EQ> fnw_nfk = fnw_nf/pc

COMMENT> Capital Account

COMMENT> gross fixed capital formation (buildings and dwellings)
IDENTITY> i_bd_nfc
EQ> i_bd_nfc = i_bd_nfc_k * p_bd

COMMENT> 
IDENTITY> i_equip_nfc
EQ> i_equip_nfc = i_equip_nfc_k * p_equip

COMMENT>  Real net stock of buildings and dwellings
IDENTITY> bd_nfc_k
EQ> TSDELTA(bd_nfc_k) = i_bd_nfc_k - TSLAG(bd_nfc_k,1) * delta_bd_nfc

COMMENT> Real net stock of equipment
IDENTITY> equip_nfc_k
EQ> TSDELTA(equip_nfc_k) = i_equip_nfc_k - TSLAG(equip_nfc_k,1) * delta_equip_nfc

COMMENT> Nominal net stock of buildings and dwellings
IDENTITY> bd_nfc
EQ> TSDELTA(bd_nfc) = i_bd_nfc + TSLAG(bd_nfc_k,1) * (1-delta_bd_nfc)*TSDELTA(p_bd) - TSLAG(bd_nfc_k,1) * delta_bd_nfc * p_bd

COMMENT> Nominal net stock of equipment
IDENTITY> equip_nfc
EQ> TSDELTA(equip_nfc) = i_equip_nfc + TSLAG(equip_nfc_k,1) * (1-delta_equip_nfc)*TSDELTA(p_equip) - TSLAG(equip_nfc_k,1) * delta_equip_nfc * p_equip

COMMENT> FINANCIAL CORP

COMMENT> Real side

COMMENT> 
IDENTITY> int_f
EQ> int_f = (TSLAG(idep,1)*TSLAG(iba_f,1) + TSLAG(iloan,1)*TSLAG(l_f,1) + TSLAG(ibd,1)*TSLAG(sec_f_d,1) + TSLAG(iboa,1)*TSLAG(sec_f_a,1))

COMMENT> 
IDENTITY> div_f
EQ> div_f = d_20124 *(((TSLAG(eq_f_a_f,1) + TSLAG(eq_nf_a_nf,1)) - (TSLAG(eq_f_l_f,1) + TSLAG(eq_h_f ,1)+ TSLAG(eq_row_a_f,1) + TSLAG(eq_nf_a_f,1) + TSLAG(eq_g_f,1)))* TSLAG(divd,1) + TSLAG(eq_f_a_row,1)*TSLAG(diva,1)) + (1-d_20124)*((TSLAG(neq_f,1)*TSLAG(divd,1))) +  div_f_adj

COMMENT> 
IDENTITY> insu_f
EQ> insu_f = TSLAG(ins_f,1)*TSLAG(insu,1)

COMMENT> 
IDENTITY> propinc_r_f
EQ> propinc_r_f = int_r_f + div_r_f + ins_r_f + res_r_f

>>>>

## Changes to wage equation
growth_mean_dp_regul= (mean_dp_regul/TSLAG(mean_dp_regul,4)) - 1

growth_mean_dp_regul_t= ts(c(0,0,0, growth_mean_dp_regul), start = c(2005,3), frequency = 4 )

wage_ds_t_growth= 0.5*inflation_t+0.5*growth_mean_dp_regul_t

wage_ds_t_new= sd1* wage_ds*(1+wage_ds_t_growth) + sd2* TSLAG(wage_ds,1)*(1+TSLAG(wage_ds_t_growth,1)) + sd3* TSLAG(wage_ds,2)*(1+TSLAG(wage_ds_t_growth,2)) + sd4* TSLAG(wage_ds,3)*(1+TSLAG(wage_ds_t_growth,3))
wage_gap= wage_ds_t - mean_dp_regul

@@
